---
title: "Simple Example"
author: "Your Name"
date: "`r Sys.Date()`"
output: 
  html_document: 
    df_print: paged
---

```{r setup, include=FALSE}
# Load necessary libraries
library(ggplot2)
```

## Introduction

This is a simple example using the built-in `mtcars` dataset in R. We will perform basic operations on the dataset and create a plot with `ggplot2`.

## Basic Operations

Let's start by taking a quick look at the `mtcars` dataset.

```{r}
# Print the first few rows of the dataset
head(mtcars)
```

Now let's perform a basic summary of the dataset.

```{r}
# Summary statistics of the dataset
summary(mtcars)
```

## Creating a Simple Plot

We will now create a scatter plot using the `mpg` (miles per gallon) and `hp` (horsepower) variables from the `mtcars` dataset.

```{r}
# Create a scatter plot of mpg vs hp
ggplot(mtcars, aes(x = hp, y = mpg)) +
  geom_point() +
  labs(title = "Scatter Plot of Horsepower vs. MPG",
       x = "Horsepower",
       y = "Miles Per Gallon (MPG)") +
  theme_minimal()
```
